---
title: "Social Network Analysis <br/> Home Assignment 3"
author: '{Your Name}'
date: "due date - 05.06.2017 23:59"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---
# Network communities
Please send your reports to hse.ntwks@gmail.com with the subject of of the following structure:<br/>
*[MAGOLEGO SNA 2017] {LastName} {First Name} HW{Number}*

Late submission policy: -1 point per day

Use this file as a template for your report.\
Support your computations with figures and comments. Send ONLY .Rmd versions of your report.

```{r, echo=FALSE}
library(igraph)
```


## Yahoo Music Network

For this assignment, you have to load [the part of Yahoo Music Network](https://drive.google.com/file/d/0Bwd5a7NScgMtNElfOFdSbE1UYnM/view). Archive contains network in GML format and corresponding list of artists.

```{r}
## Put your code here
 g<-read.graph("music2K.gml",format=c("gml"))
labe <- read.table("artists.txt",sep = "
                   ")
labe$V1=as.character(labe$V1)
V(g)$name=labe$V1
```

Edges in this network appear if enough number of users have given ratings to both music bands. Note, that edges are weighted with similarity of the ratings.


### 1. Preprocessing

This network needs to be preprocessed. Do the steps, described on seminar, to make it look properly. How many vertices and edges were deleted?

```{r}
## Put your code here
summary(g)
g2 = delete.vertices(g, degree(g) == 0)
g2=simplify(g2)
summary(g2)
```
In second graph we removed 4 isolated nodes, because they don't have connections and there are no self-loops.

### 2. Clustering

Define clusters for this networks using one of the algorithms described on lectures and seminars:
```{r}
## Put your code here
com <- fastgreedy.community(g2)
```

Compute density of obtained clusters:
```{r}
densi <- 1:length(com)
internal <-  1:length(com)
for (i in 1:length(com)) {
  gg <- induced.subgraph(g2, which(com$membership == i))
  internal[i] <- ecount(gg)
  densi[i] <- graph.density(gg)
}
densi

```

Compute the ratio of inner clusters connections to outer ones:
```{r}
sum(internal) / ecount(g2)

```


### 3. Visualization & interpretation

Visulize five of the most dense clusters. Use names of artists as node labels on the graph.
```{r}
densed <- which(densi %in% sort(densi, decreasing = TRUE)[1:5])
t <- which(com$membership %in% densed)
subg <- induced.subgraph(g2, which(membership(com) == 19&23&25&26&27))

plot(subg,vertex.label=V(subg)$name)
```

<b> (Extra task) </b>Try to interpret (using Wikipedia or other resources) obtained clusters.

Relying on information in wiki, I could say that they differentiate by genre.